### 2020-11-27 ms.tex
Initial commit

\documentclass[fleqn,usenatbib]{mnras}

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\DeclareRobustCommand{\VAN}[3]{#2}
\let\VANthebibliography\thebibliography
\def\thebibliography{\DeclareRobustCommand{\VAN}[3]{##3}\VANthebibliography}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Artificial Pulsar]{Tuning Low Frequency Pulsar Searching with an  Artificial Pulsar Device}

\author[J.-H. Gu et al.]{
Junhua Gu$^{1}$\thanks{E-mail: jhgu@nao.cas.cn} et al.
\\
% List of institutions
$^{1}$National Astronomical Observatories, Chinese Academy of Sciences, 20A Datun Road, Beijing, China
}
% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2021}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Abstract
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{Methods, Observations, Simulations etc.}

\section{Conclusions}

\section*{Acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{mnras}
\bibliography{ms}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2020-11-28 ms.tex
Updates from Overleaf

@@
 \usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
+%\usepackage{amssymb}	% Extra maths symbols
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction}
+\citet{2017AAS...22915516P}, \citet{2011AAS...21723406S}
 
-%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%
+\section{Artificial Pulsar Device}
+The artificial pulsar device (APD hereafter) is a device that is able to emit simulated pulsar signal within some certain bandpass.
+We design it to be able to simulate the dispersion effect and arbitrary pulse profile of a pulsar.
+Our implementation of APD is composed of three modules: 1) a high performance workstation that is responsible of computing the pulsar signal online, 2) a software-defined radio transmitter that receives the command from the workstation and convert it to voltage signal, which is then fed into 3) a radio frequency front-end.
+The radio frequency front-end is further composed of a radio frequency power amplifier (RFPA hereafter) and an antenna that is used to broadcast the actual signal.
 
-\section{Introduction}
+The APD can be placed near the low-frequency pulsar observation device (LFPOD hereafter). 
+It is not necessary for the emitting antenna to be placed inside the range of the primary beam LFPOD.
+The power of the emitted signal can be amplified to a high enough level so that when the signal is received by the LFPOD from its side lobes it approximates the power level of a natural pulsar.
 
-\section{Methods, Observations, Simulations etc.}
+\subsection{Computing Artificial Pulsar Signal}
+
+\subsection{Emitting Generated Signal}
+
+\section{An Example of Tuning}
+
+\section{Discussion}
 
@@
 
-% End of mnras_template.tex
+% End of ms.tex

### 2020-11-28 ms.tex
Updates from Overleaf

@@
 We design it to be able to simulate the dispersion effect and arbitrary pulse profile of a pulsar.
-Our implementation of APD is composed of three modules: 1) a high performance workstation that is responsible of computing the pulsar signal online, 2) a software-defined radio transmitter that receives the command from the workstation and convert it to voltage signal, which is then fed into 3) a radio frequency front-end.
-The radio frequency front-end is further composed of a radio frequency power amplifier (RFPA hereafter) and an antenna that is used to broadcast the actual signal.
+Our implementation of APD is composed of three modules: 1) a high performance workstation that is responsible of computing the pulsar signal online, 2) a software-defined radio (SDR) transmitter that accepts commands and data stream from the workstation and convert it to voltage signal, which is then fed into 3) a radio frequency front-end.
+The radio frequency front-end is further composed of a radio frequency power amplifier (PA hereafter) and an antenna that is used to broadcast the actual signal.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{flow_chart.pdf}
+    \caption{The flow chart of emitting the simulated pulsar signal.
+    }
+    \label{fig:flow_chart}
+\end{figure}
 
 The APD can be placed near the low-frequency pulsar observation device (LFPOD hereafter). 
-It is not necessary for the emitting antenna to be placed inside the range of the primary beam LFPOD.
+Though possible, it is not necessary for the emitting antenna to be placed inside the range of the primary beam LFPOD.
 The power of the emitted signal can be amplified to a high enough level so that when the signal is received by the LFPOD from its side lobes it approximates the power level of a natural pulsar.
 
+In this section, we describe the algorithms and steps that are used to generate the radio frequency signal, which is later used to tune LFPODs.
+
 \subsection{Computing Artificial Pulsar Signal}
+\subsubsection{Generating filterbank data before dispersion}
+The pulse amplitude profile $f$ is related to two variables: frequency $\nu$ and pulse phase $\theta$, where $\theta\in[-0.5, 0.5]$.
+Given that the bandwidth is not extremely width, it is a good enough assumption that the frequency part and the phase part can be separated as
+\begin{gather}
+    f(\nu,\theta)=S(\nu)p(\theta),
+\end{gather}
+where $S$ is the spectrum and $p$ is the pure phase-related part.
+In following sections, we simply assume $S(\nu)\equiv 1$. 
+When in actual experiments, no further cost is needed if we introduce a non-trivial $S(\nu)$.
 

### 2020-11-28 ms.tex
new file:   dm0_profile.pdf 	new file:   dm10_profile.pdf 	new file:   dm1_profile.pdf 	modified:   ms.tex

@@
 \usepackage{graphicx}	% Including figure files
+\usepackage{pict2e}
 \usepackage{amsmath}	% Advanced maths commands
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\columnwidth]{dm0_profile.pdf}
+    \caption{Frequency dependent pulse profile before the dispersion effect is applied. 
+    The period is set to be 20 ms and the amplitude profile is described a gaussian function with $\sigma=0.05$}
+    \label{fig:dm0_profile}
+ \end{figure}
+
+ \begin{figure}
+    \centering
+    \includegraphics[width=0.9\columnwidth]{dm10_profile.pdf}
+    \caption{Frequency dependent pulse profile with a $DM=10$ dispersion effect applied. The parameter of the pulsar
+    is same as the one used in Figure \ref{fig:dm0_profile}}
+    \label{fig:dm10_profile}
+ \end{figure}
+
 \subsection{Emitting Generated Signal}

### 2020-11-29 ms.tex
Updates from Overleaf

@@
 \subsubsection{Generating filterbank data before dispersion}
-The pulse amplitude profile $f$ is related to two variables: frequency $\nu$ and pulse phase $\theta$, where $\theta\in[-0.5, 0.5]$.
+The pulse amplitude profile $f$ is related to two variables: frequency $\nu$ and pulse phase $\theta$ and it meets
+\begin{gather}
+    f(\nu, \theta+1)=f(\nu, \theta)
+\end{gather}
 Given that the bandwidth is not extremely width, it is a good enough assumption that the frequency part and the phase part can be separated as
@@
 In following sections, we simply assume $S(\nu)\equiv 1$. 
-When in actual experiments, no further cost is needed if we introduce a non-trivial $S(\nu)$.
+When in actual experiments, no further cost is required if we introduce a non-trivial $S(\nu)$.
+
+By assuming 
+\begin{gather}
+    p(\theta)=\left \{
+    \begin{array}{rl}
+        p(\theta-1) &\theta \geq 0.5\\
+         \exp(-\frac{\theta^2}{2w^2}) & \theta\in[-0.5, 0.5) \\
+        p(\theta+1) &\theta < -0.5\\
+    \end{array}
+    \right ., 
+\end{gather}
+we calculate an example of the frequency-dependent pulse profile of a fake pulsar with period assumed to be 20 ms, as is shown in Figure \ref{fig:dm0_profile}.
+The frequency range is assumed to be 150-200 MHz here.
 
@@
     \caption{Frequency dependent pulse profile before the dispersion effect is applied. 
-    The period is set to be 20 ms and the amplitude profile is described a gaussian function with $\sigma=0.05$}
+    The period is set to be 20 ms and the amplitude profile is described a Gaussian function with $w=0.05$}
     \label{fig:dm0_profile}
  \end{figure}
+
+ Then we need to apply the effects of dispersion to the pulse signal.
+According to e.g., \citet{2012hpa..book.....L}, the delay of frequency $\nu$ that is caused by the dispersion can be calculated as
+ \begin{gather}
+     \Delta t(\nu)\simeq 4.15\times 10^6~{\rm ms}~\left(\frac{{\rm MHz}}{\nu}\right)^2\frac{\rm DM}{\rm pc~cm^{-3}}.
+ \end{gather}
+ So that the frequency dependent pulse profile after the dispersion effect is applied can be calculated as
+ \begin{gather}
+     f^{\rm d}(\nu, \theta)=f(\nu, \theta-\Delta t(\nu)/\tau),
+ \end{gather}
+where $\tau$ is the period of the pulsar. 
+We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm10_profile}.
+The DM is assumed to be 10.0 and other parameters are same as what we set in Figure \ref{fig:dm0_profile}.
 
@@
     \includegraphics[width=0.9\columnwidth]{dm10_profile.pdf}
-    \caption{Frequency dependent pulse profile with a $DM=10$ dispersion effect applied. The parameter of the pulsar
+    \caption{Frequency dependent pulse profile with a $\rm DM=10$ dispersion effect applied. The parameter of the pulsar
     is same as the one used in Figure \ref{fig:dm0_profile}}
@@
  \end{figure}
+
+With the amplitude profile in hand, we go on to generate the narrow band in-phase and quadrature (I/Q hereafter) signals.
+First we determine the sampling interval $dt$ of the final generated I/Q time series signal and the number of frequency channels to $N_{\rm ch}$ be used in follow up procession.
+The number of frequency channels further determines the bandwidth of each frequey channel as
+\begin{gather}
+    d\nu=\frac{f_{\max}-f_{\min}}{N_{\rm ch}}.
+\end{gather}
+For the sampling interval $dt$, according to the Nyquist Theorem the upper limit of which has to be $\frac{1}{2BW}$. 
+For we are using I/Q sampling here the upper limit of the sampling interval is enlarged to $1/BW$.
+The sampling interval of the narrow band I/Q data for current step can be calculated as
+\begin{gather}
+ dT=\frac{dt}{2N_{\rm ch}}.
+\end{gather}
+The factor 2 in the denominator is oversampling factor that we choose.
+Thus the number of time bins within each period is determined 
+\begin{gather}
+ N_{\rm t}=\left\lfloor\frac{\tau}{dT}\right\rfloor.
+\end{gather}
+Note that in order to achieve a high computing performance, we limit the actual period $\tau$ can only be an integer multiple of $dT$.
+
+So that for each frequency bin and time bin in a single period, we can calculate its instant complex voltage as
+\begin{gather}
+    U(\nu_{j}, t_{k})=\frac{1}{2}f^{\rm d}(\nu_j, t_{k}/\tau)(x^{\rm re}(j,k)+x^{\rm im}(j,k)i),
+\end{gather}
+where $j=1..N_{\rm ch}$, $k=1..N_{t}$, $i^2=-1$, and each $x^{\rm re}$ and $x^{\rm re}$ follows a standard normal distribution $\mathcal{N}(0,1)$ independently.
+
+The narrow band I/Q data is then fed into a over-sampled polyphase filterbank (PFB) to synthesize a broadband base-band I/Q data stream.
+We take the work of \citet{2020JAI.....950004M} as a reference of designing the PFB.
+We set the number of channels to be $N_{\rm ch}=16384$ and the taps of each channel to be 12.
+PFBs are a kind of standard digital signal processing steps, so we just skip the details of the PFB that we use in this work.
+
+The PFB outputs the baseband I/Q sampling time series, which is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
+The RF signal is fed into a power amplifier and broadcast through a proper antenna.
 

### 2020-12-03 ms.tex
Updates from Overleaf

@@
 
+ \subsubsection{Applying the dispersion effect}
+
  Then we need to apply the effects of dispersion to the pulse signal.
@@
 where $\tau$ is the period of the pulsar. 
-We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm10_profile}.
+We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm1_profile}.
 The DM is assumed to be 10.0 and other parameters are same as what we set in Figure \ref{fig:dm0_profile}.
@@
     \centering
-    \includegraphics[width=0.9\columnwidth]{dm10_profile.pdf}
-    \caption{Frequency dependent pulse profile with a $\rm DM=10$ dispersion effect applied. The parameter of the pulsar
+    \includegraphics[width=0.9\columnwidth]{dm1_profile.pdf}
+    \caption{Frequency dependent pulse profile with a $\rm DM=1$ pc cm$^{-3}$ dispersion effect applied. The parameter of the pulsar
     is same as the one used in Figure \ref{fig:dm0_profile}}
-    \label{fig:dm10_profile}
+    \label{fig:dm1_profile}
  \end{figure}
+
+\subsubsection{Generating the narrow band I/Q sampling data}
 
@@
 
+\subsubsection{Generating baseband I/Q sampling data stream}
+
 The narrow band I/Q data is then fed into a over-sampled polyphase filterbank (PFB) to synthesize a broadband base-band I/Q data stream.
@@
 
-The PFB outputs the baseband I/Q sampling time series, which is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
+The PFB outputs the baseband I/Q sampling time series.
+We plot a sample of the baseband I/Q sample data in Figure \ref{fig:iq_data}(a), the DM of which is $1$ pc cm$^{-3}$.
+It is obvious that all apparent time domain feature has been smeared because of the dispersion, so that pure time domain analysis is hardly possible to detect the fake pulsar we simulated here.
+As a comparison, we present the same plot of the I/Q data with DM=0 pc cm$^{-3}$ in Figure \ref{fig:iq_data}(b), in which pulse-like time domain structure can be recognized clearly.
+The I/Q sampling data stream is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
 The RF signal is fed into a power amplifier and broadcast through a proper antenna.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.95\columnwidth]{dm1_iq.pdf}\\
+    \includegraphics[width=0.95\columnwidth]{dm0_iq.pdf}
+    \caption{The real part of the baseband I/Q data as a function of time.
+Two periods are shown here.
+The period is set to be 20 ms, in (a) the DM is set to be 10 pc cm$^{-3}$ and in (b), the DM is set to be 0 pc cm$^{-3}$ for the purpose of comparison.}
+    \label{fig:iq_data}
+\end{figure}
 

### 2020-12-05 ms.tex
Updates from Overleaf

@@
 
+\subsection{Important Approximations that We Make}
+The purpose of this work is to present a method of tuning the search of pulsars in low frequency radio band, which is composed of signal receiving/recording and signal detection.
+Dedispersion is an important step in the signal detection stage.
+According to e.g., \citet{2012hpa..book.....L}, it is possible to perform either coherent dedispersion or incoherent dedispersion.
+The former works on raw baseband data and the latter works on channelized filterbank data.
+The main different between these two category of dedispersion methods is whether phase information is kept in the input data.
+In order to enable the generated signal suitable to both category of dedispersion methods, we have to ensure that the phase information is treated with caution.
+Considering that fact that the dispersion caused by ISM can cause delays of different frequencies in low frequency band to reach at most $10^2$ s time scale, computing the dispersed pulsar signal online without necessary approximation is infeasible.
+
+We make following approximation when generating the artificial pulsar signal: the pulsar signal (not only the amplitude profile, but also the signal phase) repeats with a period of $n\tau$, where $\tau$ is the period of the pulsar, $n$ is an integer.
+The value of $n$ is chosen so that it is affordable by the computation resource of the workstation that we use to generate the signal and large enough to ensure good enough statistics in folding.
+With above approximation the frequency components contained in the signal become discrete so that the phase delays of all the frequency components can be computed precisely.
+
+In practice, we choose the value of $n\tau$ around $1$ s.
+As the signal can be computed offline, this value can reach several seconds to dozens of seconds.
+If incoherent dedispersion method is used, it is also possible to update the repeating signal samples every tens of seconds (this time interval is determined by computing performance), for the phase information is not important.
+
 \subsection{Computing Artificial Pulsar Signal}
-\subsubsection{Generating filterbank data before dispersion}
-The pulse amplitude profile $f$ is related to two variables: frequency $\nu$ and pulse phase $\theta$ and it meets
+\subsubsection{Generating baseband I/Q samples}
+The pulse amplitude profile $f(\theta)$, where $\theta$ is the pulse phase should meet following constraint
 \begin{gather}
-    f(\nu, \theta+1)=f(\nu, \theta)
+    f(\theta+1)=f(\theta).
 \end{gather}
-Given that the bandwidth is not extremely width, it is a good enough assumption that the frequency part and the phase part can be separated as
+In following sections we utilize a Gaussian function with a pulse width parameter $w$ to describe the profile:
 \begin{gather}
-    f(\nu,\theta)=S(\nu)p(\theta),
+    f(\theta)=\left \{
+    \begin{array}{rl}
+        f(\theta-1) &\theta \geq 0.5\\
+         \exp(-\frac{\theta^2}{2w^2}) & \theta\in[-0.5, 0.5) \\
+        f(\theta+1) &\theta < -0.5\\
+    \end{array}
+    \right ..
 \end{gather}
-where $S$ is the spectrum and $p$ is the pure phase-related part.
-In following sections, we simply assume $S(\nu)\equiv 1$. 
-When in actual experiments, no further cost is required if we introduce a non-trivial $S(\nu)$.
-
-By assuming 
+Assuming a frequency range of $[\nu_{\min}, \nu_{\max}]$, the sampling interval $dt$ is also fixed as $dt=1/B$, where $B=\nu_{\max}-\nu_{\min}$.
+Thus the baseband I/Q sample series is generated as 
 \begin{gather}
-    p(\theta)=\left \{
-    \begin{array}{rl}
-        p(\theta-1) &\theta \geq 0.5\\
-         \exp(-\frac{\theta^2}{2w^2}) & \theta\in[-0.5, 0.5) \\
-        p(\theta+1) &\theta < -0.5\\
-    \end{array}
-    \right ., 
+    y_j=f(\frac{j\times dt}{\tau})\frac{x^{\rm re}_j+x^{\rm im}_ji}{2}, j=1..\left \lfloor\frac{n\tau}{dt} \right\rfloor
 \end{gather}
-we calculate an example of the frequency-dependent pulse profile of a fake pulsar with period assumed to be 20 ms, as is shown in Figure \ref{fig:dm0_profile}.
-The frequency range is assumed to be 150-200 MHz here.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\columnwidth]{dm0_profile.pdf}
-    \caption{Frequency dependent pulse profile before the dispersion effect is applied. 
-    The period is set to be 20 ms and the amplitude profile is described a Gaussian function with $w=0.05$}
-    \label{fig:dm0_profile}
- \end{figure}
+where each $x^{\rm re}$'s and $x^{\rm im}$'s independently follows a standard normal distribution.
 
  \subsubsection{Applying the dispersion effect}
-
- Then we need to apply the effects of dispersion to the pulse signal.
-According to e.g., \citet{2012hpa..book.....L}, the delay of frequency $\nu$ that is caused by the dispersion can be calculated as
+  Applying the ISM dispersion effect is simply an inverse operation of coherent dedispersion with some slight differences.
+  According to e.g., \citet{2012hpa..book.....L}, we calculate the dispersed baseband I/Q sample series as
   \begin{gather}
-     \Delta t(\nu)\simeq 4.15\times 10^6~{\rm ms}~\left(\frac{{\rm MHz}}{\nu}\right)^2\frac{\rm DM}{\rm pc~cm^{-3}}.
+      \mathbf{y}^d={\rm IDFT}(\mathbf{Y}^d)
   \end{gather}
- So that the frequency dependent pulse profile after the dispersion effect is applied can be calculated as
   \begin{gather}
-     f^{\rm d}(\nu, \theta)=f(\nu, \theta-\Delta t(\nu)/\tau),
+      Y_j^d={\rm DFT}(\mathbf{y})_j\exp(2\pi i \nu_j\Delta t(\nu_j)),
   \end{gather}
-where $\tau$ is the period of the pulsar. 
-We show an example of frequency-dependent pulse profile after the dispersion effect is applied in Figure \ref{fig:dm1_profile}.
-The DM is assumed to be 10.0 and other parameters are same as what we set in Figure \ref{fig:dm0_profile}.
+  where ${\rm DFT}$ and ${\rm IDFT}$ denote the forward and backward discrete Fourier transform, respectively, $\mathbf{y}$ is a vector with each of its element to be $y_j$, $\mathbf{Y}$ is a vector with each of its element to be $\mathbf{Y}_j$, $\nu_j$ is the frequency corresponding to the $j$-th frequency channel, and the delay cause by the dispersion is calculated as
+  \begin{gather}
+     \Delta t(\nu)\simeq 4.15\times 10^6~{\rm ms}~\left(\frac{{\rm MHz}}{\nu}\right)^2\frac{\rm DM}{\rm pc~cm^{-3}},
+ \end{gather}
+ according to e.g., \citet{2012hpa..book.....L}.
 

### 2020-12-10 ms.tex
new file:   dm0_fb.pdf 	modified:   dm0_iq.pdf 	deleted:    dm0_profile.pdf 	modified:   dm1_iq.pdf 	deleted:    dm1_profile.pdf 	modified:   ms.tex
Updates from Overleaf

@@
 
- \begin{figure}
+ We present two examples of the time domain I/Q sampling data in Figure \ref{fig:iq_data} with ${\rm DM}=0$ pc~cm$^{-3}$ and DM=1 pc~cm$^{-3}$, respectively.
+ The frequency range is set to be $100\sim 200$ MHz.
+ Apparently the wide bandwidth and the low central frequency make the time domain data rather sensitive to the dispersion measure.
+ ${\rm DM}=1$ is a rather small value of the dispersion measure among known pulsars.
+ When trying to detect pulsars with larger dispersion measures in low frequency radio band, difficulties will appear caused by the the dispersion of ISM more seriously compared with higher radio bands.
+
+\begin{figure*}
     \centering
-    \includegraphics[width=0.9\columnwidth]{dm1_profile.pdf}
-    \caption{Frequency dependent pulse profile with a $\rm DM=1$ pc cm$^{-3}$ dispersion effect applied. The parameter of the pulsar
-    is same as the one used in Figure \ref{fig:dm0_profile}}
-    \label{fig:dm1_profile}
- \end{figure}
-
-\subsubsection{Generating the narrow band I/Q sampling data}
-
-With the amplitude profile in hand, we go on to generate the narrow band in-phase and quadrature (I/Q hereafter) signals.
-First we determine the sampling interval $dt$ of the final generated I/Q time series signal and the number of frequency channels to $N_{\rm ch}$ be used in follow up procession.
-The number of frequency channels further determines the bandwidth of each frequey channel as
-\begin{gather}
-    d\nu=\frac{f_{\max}-f_{\min}}{N_{\rm ch}}.
-\end{gather}
-For the sampling interval $dt$, according to the Nyquist Theorem the upper limit of which has to be $\frac{1}{2BW}$. 
-For we are using I/Q sampling here the upper limit of the sampling interval is enlarged to $1/BW$.
-The sampling interval of the narrow band I/Q data for current step can be calculated as
-\begin{gather}
- dT=\frac{dt}{2N_{\rm ch}}.
-\end{gather}
-The factor 2 in the denominator is oversampling factor that we choose.
-Thus the number of time bins within each period is determined 
-\begin{gather}
- N_{\rm t}=\left\lfloor\frac{\tau}{dT}\right\rfloor.
-\end{gather}
-Note that in order to achieve a high computing performance, we limit the actual period $\tau$ can only be an integer multiple of $dT$.
-
-So that for each frequency bin and time bin in a single period, we can calculate its instant complex voltage as
-\begin{gather}
-    U(\nu_{j}, t_{k})=\frac{1}{2}f^{\rm d}(\nu_j, t_{k}/\tau)(x^{\rm re}(j,k)+x^{\rm im}(j,k)i),
-\end{gather}
-where $j=1..N_{\rm ch}$, $k=1..N_{t}$, $i^2=-1$, and each $x^{\rm re}$ and $x^{\rm re}$ follows a standard normal distribution $\mathcal{N}(0,1)$ independently.
-
-\subsubsection{Generating baseband I/Q sampling data stream}
-
-The narrow band I/Q data is then fed into a over-sampled polyphase filterbank (PFB) to synthesize a broadband base-band I/Q data stream.
-We take the work of \citet{2020JAI.....950004M} as a reference of designing the PFB.
-We set the number of channels to be $N_{\rm ch}=16384$ and the taps of each channel to be 12.
-PFBs are a kind of standard digital signal processing steps, so we just skip the details of the PFB that we use in this work.
-
-The PFB outputs the baseband I/Q sampling time series.
-We plot a sample of the baseband I/Q sample data in Figure \ref{fig:iq_data}(a), the DM of which is $1$ pc cm$^{-3}$.
-It is obvious that all apparent time domain feature has been smeared because of the dispersion, so that pure time domain analysis is hardly possible to detect the fake pulsar we simulated here.
-As a comparison, we present the same plot of the I/Q data with DM=0 pc cm$^{-3}$ in Figure \ref{fig:iq_data}(b), in which pulse-like time domain structure can be recognized clearly.
-The I/Q sampling data stream is then sent to an SDR transmitter so that actual radio frequency (RF) signal within desired frequency range is generated continuously.
-The RF signal is fed into a power amplifier and broadcast through a proper antenna.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.95\columnwidth]{dm1_iq.pdf}\\
     \includegraphics[width=0.95\columnwidth]{dm0_iq.pdf}
+    \includegraphics[width=0.95\columnwidth]{dm1_iq.pdf}
     \caption{The real part of the baseband I/Q data as a function of time.
@@
     \label{fig:iq_data}
+\end{figure*}
+
+We show the waterfall chart of above generated time domain I/Q data in Figure \ref{fig:fb} to inspect the frequency-dependent profile.
+The waterfall chart is generated by feeding the time domain I/Q data stream into a polyphase filterbank.
+Apparently for the ${\rm DM}=1$ pc~cm$^{-3}$ signal, lower frequency has larger delay, which agrees with properties of dispersion effect caused by ISM. 
+This verifies the correctness of the signal we generated.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.9\columnwidth]{dm0_fb.pdf}
+    \includegraphics[width=0.9\columnwidth]{dm1_fb.pdf}
+    \caption{Frequency dependent pulse profile with a $\rm DM=0$ pc cm$^{-3}$ dispersion effect applied}
+    \label{fig:fb}
+\end{figure*}
+
+\subsection{Emitting Generated Signal}
+The generated broadband I/Q data stream that has been dispersed is then fed into some radio frequency transmitter.
+We use the software defined radio (SDR) transceiver \textit{USRP} X310\footnote{\url{https://kb.ettus.com/X300/X310}} to send the generated signal.
+The maximum sample rate can reach 200 Msps, while we use a sample rate of 100 Msps corresponding to a bandwidth of $B=100$ MHz.
+The corresponding frequency range is then $[\nu_c-B/2, \nu_c+B/2]$, where $\nu_c$ is the central frequency.
+The SDR transceiver is connected to a high performance workstation through a 10Gb Ethernet fiber.
+In this work we set the central frequency $\nu_c=150$ MHz, so that the frequency range is $100\sim 200$ MHz.
+
+There are other choices of devices that can be used to transmit the generated signal, e.g.,  \textit{LimeSDR}\footnote{\url{https://limemicro.com/products/boards/limesdr}}, 
+\textit{HackRF}\footnote{\url{https://greatscottgadgets.com/hackrf}}, and other general purpose digital-analog converter cards. 
+The reason why choose \textit{USRP} X310 is its maximum instant bandwidth of 200 MHz, which enables us to emulate the conditions of most of current working low frequency radio telescopes.
+
+The generated radio frequency signal is then amplified and broadcast through an antenna of the corresponding frequency range.
+Before broadcasting and receive the signal through antennas, we use an oscilloscope to check the voltage signal at the output terminal of the SDR transceiver as are shown in \ref{fig:osc_trace}.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.45\columnwidth]{dm_0_trace.eps}
+    \includegraphics[width=0.45\columnwidth]{dm_0.05_trace.eps}
+    \caption{The voltage signal trace observed with an oscilloscope at the output terminal of the SDR transceiver.
+The left and the right panel show signals with ${\rm DM}=0$ pc~cm$^{-3}$ and ${\rm DM}=0.05$ pc~cm$^{-3}$, respectively.
+The periods of both signals are set to be $20$ ms.
+Note that the lower limits of the frequency range of the generated signals are 100 MHz.}
+    \label{fig:osc_trace}
 \end{figure}
 
-\subsection{Emitting Generated Signal}
+\section{Two Examples of Tuning}
+We set up two experiments to demonstrate the process of tuning LFPODs to perform the pulsar signal detection. 
+One of the experiment is using the SDR transceiver as a toy LFPOD.
+Another experiment performed with the low frequency interferometer 21CMA.
+For both experiment we follow the steps as
+\begin{enumerate}
+    \item Place the emitter (i.e., the \textit{USRP} X310 transceiver) close to the LFPOD;
+    \item Set the emitter and the LFPOD to proper mode and start the data acquisition;
+    \item After enough data is acquired and stored to disk, perform a pulsar search procedure to check whether the artificial pulsar signal can be recognized;
+    \item If necessary, adjust the emitting setup.
+\end{enumerate}
 
-\section{An Example of Tuning}
+\subsection{HackRF---A Toy LFPOD}
+\subsubsection{Setup of the experiment}
+\textit{HackRF} is a low cost SDR transceiver with an operation frequency of 1 MHz$\sim$ 6 GHz.
+The maximum sample rate is 20 MHz.
+We place an \textit{HackRF} 1 m away from the emitter antenna to receive the signal.
+As the distance is close enough, we do not use any external power amplifier either for the emitter and the receiver. 
+The internal amplifier gains for the emitter and the receiver are set to 0 dB and 10 dB, respectively.
+The sample rate of the receiver is set to 10 Msps, corresponding a bandwidth of 10 MHz and the central frequency is set to 150 MHz, which leads to a frequency range of $145\sim 155$ MHz.
+The reason why we do not set the sample rate to its maximum allowed value is to prevent from packet dropping.
+
+\subsubsection{Cases that we test}
+We test two sets of artificial pulsar signal parameters, the periods of both are set to be 18 ms, and the DM's are respectively 10 pc~cm$^{-3}$ and 10 pc~cm$^{-3}$.
+
+\subsubsection{Connecting the emitter and the receiver directly with a co-axis cable}
+
+\subsubsection{Sending and receiving the signal through antennas}
+Then we perform the data acquisition with the signal sent and received through antennas.
 

### 2020-12-17 ms.tex
Updates from Overleaf

@@
     \includegraphics[width=0.9\columnwidth]{dm1_fb.pdf}
-    \caption{Frequency dependent pulse profile with a $\rm DM=0$ pc cm$^{-3}$ dispersion effect applied}
+    \caption{Frequency dependent pulse profile with a $\rm DM=0$ pc cm$^{-3}$ (a) and $\rm DM=0$ pc cm$^{-3}$ (b) dispersion effect applied, respectively.}
     \label{fig:fb}
@@
     \includegraphics[width=0.45\columnwidth]{dm_0.05_trace.eps}
-    \caption{The voltage signal trace observed with an oscilloscope at the output terminal of the SDR transceiver.
+    \caption{The voltage signal trace (in yellow) observed with an oscilloscope at the output terminal of the SDR transceiver.
+The green lines are the PPS signal generated by the \textit{USRP} used to trigger the oscilloscope.
 The left and the right panel show signals with ${\rm DM}=0$ pc~cm$^{-3}$ and ${\rm DM}=0.05$ pc~cm$^{-3}$, respectively.
@@
 \subsubsection{Connecting the emitter and the receiver directly with a co-axis cable}
+We connect the emitter and receiver directly with a co-axis cable to test whether the signal generating and data acquisition sub-modules work correctly.
+We show the incoherently and coherently dedispersing and folding result in Figure \ref{fig:prepfold_direct_hackrf_dm100_18} and Figure \ref{fig:cddsp_direct_hackrf_dm100_18}, respectively.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{prepfold_direct_hackrf_dm100_18.pdf}
+    \caption{Incoherently dedispersing and folding result of the data acquired by \textit{HackRF} with the emitter and the receiver connected with a co-axis cable directly.}
+    \label{fig:prepfold_direct_hackrf_dm100_18}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{cddsp_direct_hackrf_dm100_18.pdf}
+    \caption{Coherently dedispersing and folding result of the data acquired by \textit{HackRF} with the emitter and the receiver connected with a co-axis cable directly.}
+    \label{fig:cddsp_direct_hackrf_dm100_18}
+\end{figure}
 

### 2020-12-27 ms.tex
Updates from Overleaf

@@
 In order to enable the generated signal suitable to both category of dedispersion methods, we have to ensure that the phase information is treated with caution.
-Considering that fact that the dispersion caused by ISM can cause delays of different frequencies in low frequency band to reach at most $10^2$ s time scale, computing the dispersed pulsar signal online without necessary approximation is infeasible.
+Considering the fact that the dispersion caused by ISM can cause delays of different frequencies in low frequency band to reach at most $10^2$ s time scale, computing the dispersed pulsar signal online without necessary approximation is inefficient.
 
